---
title: "Final Paper"
author: "Juan Sanchez, Jared Picco"
date: "2023-12-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
library(tidyverse)
library(dplyr)
library(plm)
library(ggplot2)
library(lmtest)
library(sandwich)
library(knitr)
library(broom)
library(readxl)
library(AER)
library(stargazer)
library(foreign)
library(Hmisc)
library(MatchIt)
library(mlogit)
library(haven)
library(estimatr)
```


# Introduction

``` {r setup, echo=FALSE}
options(scipen = 999)
movie_data <- read_excel("/Users/juansanchez/Documents/GitHub/Final_Paper_ECON_440/moviedata.xlsx")

summary(movie_data)

# Could explain why the economic impact is different
ggplot(movie_data, aes(x = month, y = revenue)) +
  geom_bar(stat = "identity", fill = "purple", color = "black") +
  labs(title = "Bar Plot of Revenue by Week",
       x = "Month",
       y = "Revenue ($)")

# Weeks
ggplot(movie_data, aes(x = tom_week_id, y = revenue)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Bar Plot of Revenue by Week",
       x = "tom_week_id",
       y = "Revenue ($)")

boxplot(movie_data$revenue)

```


# Initial regression

``` {r setup, echo=FALSE}
# Subset the data to look at only the weeks we are interested in and remove rows with NA in the budget
movie_data <- movie_data %>%
  filter(tom_week_id == "55"|tom_week_id =="54"|tom_week_id =="53"|tom_week_id =="52"|tom_week_id =="51"  & budget != NA & revenue != NA)

summary(movie_data$revenue)

# We are left with 4059 observations

# The mean has changed by not much, which makes sense because we are only taking a 4 week subset of the data

# We want to remove extreme outliers that skew our data

boxplot(movie_data$revenue)

Q <- quantile(movie_data$revenue, probs=c(.25, .75), na.rm = FALSE)

iqr <- IQR(movie_data$revenue)

up <-  Q[2]+3*iqr # Upper Range  
low<- Q[1]-3*iqr # Lower Range﻿

movie_data_no_outliers <- subset(movie_data, movie_data$revenue > (Q[1] - 3*iqr) & movie_data$revenue < (Q[2]+3*iqr))

# Plot the revenue by week

ggplot(movie_data_no_outliers, aes(x = week, y = revenue)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "blue", data = subset(movie_data, tom_week_id == "53"|tom_week_id == "52"|tom_week_id == "51")) +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", data = subset(movie_data, tom_week_id == "55") +
  labs(title = "Revenue by Week", x = "week", y = "log(Revenue/Budget)")

# Using tom_week_id

ggplot(movie_data, aes(x = tom_week_id, y = revenue)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "blue", data = subset(movie_data, tom_week_id == "53"|tom_week_id == "52"|tom_week_id == "51")) +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", data = subset(movie_data, tom_week_id == "55") +
  labs(title = "Revenue by Week", x = "tom_week_id", y = "log(Revenue/Budget)")




# Run a OLS regression with revenue on tom_week_id

# Run an OLS regression with the log of revenue/budget on week released and the treatment
ols_model <- lm_robust(revenue ~  tom_week_id, data = movie_data)



```





# Changed the week variable to tom_week_id because the week of year is adjusted so holidays fall on the same week.
```{r setup, echo=FALSE}

options(scipen = 999)
movie_data <- read_excel("/Users/juansanchez/Documents/GitHub/Final_Paper_ECON_440/moviedata.xlsx")

# Define the treatment
movie_data$D <- ifelse(movie_data$tom_week_id == "54"|movie_data$tom_week_id =="55", 1,0)

# Look at the summary stats of the revenue column
summary(movie_data$revenue)

# Subset the data to look at only the weeks we are interested in and remove rows with NA in the budget
movie_data <- movie_data %>%
  filter(tom_week_id == "55"|tom_week_id =="54"|tom_week_id =="53"|tom_week_id =="52"|tom_week_id =="51"  & budget != NA & revenue != NA)

# We are left with 4059 observations

# Run a OLS regression with revenue on 

# Run an OLS regression with the log of revenue/budget on week released and the treatment
ols_model <- lm_robust(log(revenue/budget) ~  week + D, data = movie_data)

#iv_reg <- ivreg(revenue ~ budget | week, data = subset_data2)

#summary(iv_reg)

summary(ols_model)

# We see that the treatment variable is statistically significant when running a linear regression with HC2 standard errors

exp(coef(ols_model))

# After exponentiating the variable from log, we see that the 




ggplot(movie_data, aes(x = tom_week_id, y = log(revenue/budget))) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "blue", data = subset(movie_data, tom_week_id == "53"|tom_week_id == "52"|tom_week_id == "51")) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", data = subset(movie_data, tom_week_id == "55"|tom_week_id == "54")) +
  labs(title = "Revenue by Week", x = "tom_week_id", y = "log(Revenue/Budget)")



```

Look at min max median and mean
```{r setup}
summary(log(movie_data$revenue)


```

# Data using a cutoff at the mean revenue
```{r setup}

subset_data <- movie_data %>%
  filter(revenue >= 2203023)


subset_data <- subset_data %>%
  filter(tom_week_id == "56"|tom_week_id =="55"|tom_week_id =="54"|tom_week_id =="53"|tom_week_id =="52" ) 



lm1 <- lm_robust(log(revenue/budget) ~ week + D, data = subset_data)
summary(lm1)


ggplot(subset_data, aes(x = tom_week_id, y = revenue))+
  geom_point(color = "blue") +  # Scatter plot
  #geom_smooth(method = "lm", se = FALSE, color = "red") +  # Line of best fit
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "purple", data = subset(subset_data, tom_week_id =="53"|tom_week_id == "52")) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", data = subset(subset_data, tom_week_id == "54"|tom_week_id =="55")) +
  labs(title = "Scatter Plot with Line of Best Fit",
       x = "tom_week_id",
       y = "log(Revenue/Budget)"
       )
```



```{r setup}
summary(subset_data$revenue)

#Important
ggplot(movie_data, aes(x = week, y = revenue)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Bar Plot of Revenue by Week",
       x = "Week",
       y = "Revenue ($)")

```

``` {r setup}

subset_data2 <- movie_data %>%
  filter(revenue >= 2203023)


subset_data2 <- subset_data2 %>%
  filter(tom_week_id == "56"|tom_week_id =="55"|tom_week_id =="54"|tom_week_id =="53"|tom_week_id =="52" ) 


#lm1 <- lm_robust(revenue ~ week, data = subset_data)
#summary(lm1)


ggplot(subset_data2, aes(x = week, y = revenue)) +
  geom_point(color = "blue") +  # Scatter plot
  #geom_smooth(method = "lm", se = FALSE, color = "red") +  # Line of best fit
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "purple", data = subset(subset_data2, tom_week_id =="53"|tom_week_id == "52")) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", data = subset(subset_data2, tom_week_id == "54"|tom_week_id =="55")) +
  labs(title = "Scatter Plot with Line of Best Fit",
       x = "Week",
       y = "Revenue ($)"
       )





```


# Copy Before
``` {r setup}

subset_data2 <- movie_data %>%
  filter(revenue >= 30000000)


subset_data2 <- subset_data2 %>%
  filter(week == "51"|week =="52"|week =="50"|week =="49")



lm1 <- lm_robust(revenue ~ week, data = subset_data)
summary(lm1)


ggplot(subset_data2, aes(x = week, y = revenue)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", se = FALSE, color = "red") +  # Line of best fit
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "purple", data = subset(subset_data2, week == "49"|week =="50")) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", data = subset(subset_data2, week == "51"|week =="52")) +
  labs(title = "Scatter Plot with Line of Best Fit",
       x = "Week",
       y = "Revenue ($)"
       )


```





movie_data <- movie_data %>%
  filter(tom_week_id == "55"|tom_week_id =="54"|tom_week_id =="53"|tom_week_id =="52"|tom_week_id =="51"  & budget != NA & revenue != NA)

data_high_rev <- movie_data %>%
  filter(revenue >= 29000000)

data_normal_rev <- movie_data %>%
  filter(revenue <= 29000000)

ols_model1_HR <- lm_robust(revenue ~  tom_week_id, data = data_high_rev)
ols_model1_NR <- lm_robust(revenue ~  tom_week_id, data = data_normal_rev)
summary(ols_model1_HR)
summary(ols_model1_NR)

ggplot(data_high_rev, aes(x = tom_week_id, y = revenue)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "blue", data = data_high_rev, tom_week_id == "52"|tom_week_id == "53") +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green", tom_week_id == "54"|tom_week_id == "55") +
  labs(title = "Revenue by Week", x = "tom_week_id", y = "Revenue")

